Updating the Feature Function Framework \titlelinebreak{} in the Moses Decoder

### 2013-07-19 mt-marathon.2013/PBML_article.tex
add appendix on how to create a new ff

% Packages
% ========
% In this place you can load required packages by the \usepackage commands.
% The following packages are loaded automatically by the class:
% euler    (for math fonts)
% graphicx (for inclusion of images)
% multicol (for multicolumn typesetting)
% natbib   (for bibliography citations)
% amssymb  (for various symbols)
% If XeLaTeX is used, fontspec and xltxtra are loaded as well.
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{tikz,gnuplot-lua-tikz}

@@

@@

>>>>

% Packages
% ========
% In this place you can load required packages by the \usepackage commands.
% The following packages are loaded automatically by the class:
% euler    (for math fonts)
% graphicx (for inclusion of images)
% multicol (for multicolumn typesetting)
% natbib   (for bibliography citations)
% amssymb  (for various symbols)
% If XeLaTeX is used, fontspec and xltxtra are loaded as well.
\usepackage{algorithmic}
\usepackage{amsmath}
\usepackage{tikz,gnuplot-lua-tikz} 
\usepackage{nameref}

@@

A detailed example of how to add a new feature function to the Moses decoder is contained in\emph{~\nameref{Appendix}}.

@@

\section*{Appendix: Adding a New Feature Function to Moses, an Example}
\label{Appendix}

The section describes how to add a new feature function to the current (July 2013) version of Moses, and use it during decoding.

\begin{enumerate}
    \item Create a new class in the decoder source code. By convention, the files should be in the folder or subfolder of either
\begin{verbatim}
   moses/FF
   moses/LM
   moses/TranslationModel
\end{verbatim}
Inherit the class from either of
\begin{verbatim}
  StatelessFeatureFunction
  StatefulFeatureFunction
\end{verbatim}
or any class that inherit from one of these classes. Other common classes to inherit from are:
\begin{verbatim}
  PhraseDictionary
  LanguageModelImplementation
\end{verbatim}

    \item Create a constructor of the form
\begin{verbatim}
  ClassName(const std::string &line);
\end{verbatim}

    \item Implement the method
\begin{verbatim}
  bool IsUseable(const FactorMask &mask) const;
\end{verbatim}
The argument is a bit vector of which factors are available. The method should return \emph{true} if it can be evaluated with these factors, otherwise return \emph{false}. If the feature does not use any factors, always return  \emph{true}.

The constructor, and this method, are the only mandatory function for feature functions. All others methods override default methods (that often do nothing).

    \item Useful methods to override:
      \begin{enumerate}
        \item If the feature needs to load data, override the method
	  \begin{verbatim}
  void Load();
	  \end{verbatim}
        \item If the feature functions takes arguments
	  \begin{verbatim}
  void SetParameter(const std::string& key, const std::string& value);
	  \end{verbatim}
\emph{name}, \emph{num-features}, \emph{tuneable} are reserved keys that the new feature should not use.
	\item If it requires initialisation and cleaning after each sentence (this is not particularly thread-safe):
	  \begin{verbatim}
  void InitializeForInput(InputType const& source);
  void CleanUpAfterSentenceProcessing(const InputType& source);
	  \end{verbatim}
       \end{enumerate}
    \item Override one or more of the Evaluate() method. 
      \begin{verbatim}
  void Evaluate(const Phrase &source
	    , const TargetPhrase &targetPhrase
	    , ScoreComponentCollection &scoreBreakdown
	    , ScoreComponentCollection &estimatedFutureScore) const;
  void Evaluate(const InputType &source
            , ScoreComponentCollection &scoreBreakdown) const;
       \end{verbatim}
Also for stateless features:
      \begin{verbatim}
  void Evaluate(const PhraseBasedFeatureContext& context,
                ScoreComponentCollection* accumulator) const;
  void EvaluateChart(const ChartBasedFeatureContext& context,
                ScoreComponentCollection* accumulator) const;
       \end{verbatim}
The method signature is similar for stateful features, but the methods return a state object:
      \begin{verbatim}
  FFState* Evaluate(const Hypothesis& cur_hypo,
		    const FFState* prev_state,
		    ScoreComponentCollection* accumulator) const;
  FFState* EvaluateChart(const ChartHypothesis&,
		      int featureID,
		      ScoreComponentCollection* accumulator) const;
      \end{verbatim}
    \item Register the new feature function with the decoder by adding the following line to \emph{Factory.cpp}:
      \begin{verbatim}
  MOSES_FNAME(ClassName);
      \end{verbatim}
    \item To instantiate the feature during decoding, add the following line to the \emph{[feature]} section of the moses.ini file:
      \begin{verbatim}
  ClassName [key=value]*
      \end{verbatim}
If it has dense features, the weights should be in the \emph{[weight]} section, for example:
      \begin{verbatim}
  ClassName0= 0.1 0.2 0.3
      \end{verbatim}

\end{enumerate}
